Target Markdown

### 2024-04-04 _targets.Rmd
Update manuscript and supplementary figures

```{targets sem-process}
list(
  tar_target(sim_fw, sim_fw_csc_rerun),
  tar_target(sim_fw_sem,
    sim_fw %>%
      as.data.frame() %>%
      mutate(across(c(stab_com, pop_stab, async, cpe, sae_total, evenness_sae,
            sae_even, cpe_int, cpe_env), log))
    ),
  tar_target(sem_eff,  sem_main_text_eff_csc_rerun),
  tar_target(sem_eff_tab, sem_main_text_eff_tab_csc_rerun),
  tar_target(sem_eff_coeff, sem_main_text_eff_tab_csc_rerun),
  tar_target(tab_sem_coeff,
    sem_main_text_coeff_csc_rerun %>%
      kable(caption = "Standardized estimates for the Structural Equation Models.") %>%
      collapse_rows(1, valign = "middle") %>%
      kable_styling()
    ),
  tar_target(sem_collinearity, sem_main_text_collinearity_csc_rerun),
  tar_target(sem_rsquared, sem_main_text_rsquared_csc_rerun),
  tar_target(tab_sem_vif,
    sem_collinearity %>%
      mutate(across(c("response", "Term"), ~var_replacement()[.x])) %>%
      mutate(VIF = round(VIF, 1)) %>%
      select(Response = response, Term, VIF) %>%
      kable(
        caption = "Variance Inflation Factor for the Structural Equation Model.") %>%
      kable_styling()
    ),
  tar_target(tab_sem_rsquared,
    sem_rsquared %>%
      rename(`$R^2$` = R.squared) %>%
      kable(caption = "Rsquared for the Structural Equation Model.") %>%
      kable_styling()
  )
)
```

@@

```{targets group-all-analysis, eval = FALSE}
list(
  tar_target(sem_main_text_tot,
    tibble(
      sim_type = c(
        "rerun",
        "non_allo",
        "rebuild",
        "no_rerun_short",
        "kno"),
      eff = list(
        sem_main_text_eff_tab_csc_rerun,
        sem_main_text_eff_tab_csc_non_allo,
        sem_main_text_eff_tab_csc_rebuild,
        sem_main_text_eff_tab_csc_kno
        ),
      rsq = list(
        sem_main_text_rquared_csc_rerun,
        sem_main_text_rquared_csc_non_allo,
        sem_main_text_rquared_csc_rebuild,
        sem_main_text_rquared_csc_kno
        ),
      collinearity = list(
        sem_main_text_collinearity_csc_rerun,
        sem_main_text_collinearity_csc_non_allo,
        sem_main_text_collinearity_csc_rebuild,
        sem_main_text_collinearity_csc_kno
        ),
    )
  ),
  tar_target(sem_main_text_eff_tab_tot,
    sem_main_text_tot %>%
      select(sim_type, eff) %>%
      unnest(cols = eff)),
  tar_target(p_sem_main_text_eff_tab_tot,
    sem_main_text_eff_tab_tot %>%
      filter(effect_type == "total") %>%
      filter(response %in% c("async", "pop_stab", "stab_com")) %>%
      filter(predictor %in% sem_tot_predictor()) %>%
      mutate(
        response = recode_factor(response, !!!var_replacement(), .ordered = TRUE),
        predictor = recode_factor(predictor, !!!var_replacement()[rev(sem_tot_predictor())], .ordered = TRUE),
        sim_type = recode_factor(sim_type, !!!sim_type_replacement(), .ordered = TRUE)
        ) %>%
      ggplot(aes(
          y = predictor,
          x = effect,
          color = response,
          shape = sim_type
        )
        ) +
      geom_point(alpha = .5) +
      scale_colour_manual(values = stab_color()) +
      scale_alpha_manual(values = stab_alpha()) +
      #  geom_hline(yintercept = 0, linetype = "dashed") +
      geom_vline(xintercept = 0, linetype = "dashed") +
      facet_grid(cols = vars(response)) +
      labs(
        x = "Total standardised effects",
        color = "Stability component",
        alpha = "Stability component"
        ) +
      theme_bw() +
      theme(
        axis.title.y = element_blank(),
        #legend.justification = "right",
        legend.position = "bottom") +
      guides(
        color = FALSE
        ) +
      theme(
        legend.title = element_blank(),
        legend.position = "bottom",
        legend.justification = c("left", "top")
      )
  )
)
```

@@

```{targets fig-stab-sr}
tar_load(default_variable_values_pred)
tar_load(model_fw_stab_comp)
tar_load(p_pred_sr_resp_div)
list(
  tar_target(richness_gradient_pred_show, seq(1, 30, length.out = 20)),
  tar_target(pred_data_show, {
    low_resp_example <- rbind(default_variable_values_pred) %>%
      as_tibble() %>%
      mutate(resp_div = .1, w_avg_tlvl = 2.0, fw_id = "new") %>%
      slice(rep(1, length(richness_gradient_pred_show))) %>%
      mutate(richness = richness_gradient_pred_show)
    high_resp_example <- rbind(default_variable_values_pred) %>%
      as_tibble() %>%
      mutate(resp_div = .9, w_avg_tlvl = 1.2, fw_id = "new") %>%
      slice(rep(1, length(richness_gradient_pred_show))) %>%
      mutate(richness = richness_gradient_pred_show)
    out <- rbind(low_resp_example, high_resp_example)
    out$stab_com <- predict(
      model_fw_stab_comp[model_fw_stab_comp$response == "stab_com", ]$model[[1]],
      out,
      allow.new.levels = TRUE
    )
    out
  }
    ),
  tar_target(p_pred_data_show_low_resp,
    pred_data_show %>%
      filter(resp_div == .1) %>%
      ggplot(aes(x = richness, y = exp(stab_com))) +
      geom_line(color = resp_div_cat_colors()["Low"]) +
      ylim(10, 25) +
      labs(x = "Species richness", y = "Community stability") +
      theme_half_open()
    ),
  tar_target(p_pred_data_show_low_resp_file,
    ggsave_multiple(
      paste0("p_pred_data_show_low_resp", c(".png", ".pdf")),
      plot = p_pred_data_show_low_resp,
      path = here::here("report", "figures"),
      scale = 1.4,
      dpi = 400,
      width = 80,
      height = 80 * .9,
      units = "mm")
    ),
  tar_target(p_pred_data_show_high_resp,
    pred_data_show %>%
      filter(resp_div == .9) %>%
      ggplot(aes(x = richness, y = exp(stab_com))) +
      geom_line(color = resp_div_cat_colors()["High"]) +
      ylim(10, 25) +
      labs(x = "Species richness", y = "Community stability") +
      theme_half_open()
    ),
  tar_target(p_pred_data_show_high_resp_file,
    ggsave_multiple(
      paste0("p_pred_data_show_high_resp", c(".png", ".pdf")),
      plot = p_pred_data_show_high_resp,
      path = here::here("report", "figures"),
      scale = 1.4,
      dpi = 400,
      width = 80,
      height = 80 * .9,
      units = "mm")
    ),
  tar_target(data_label_pred_show,
    pred_data_show %>%
      select(resp_div, richness, w_avg_tlvl) %>%
      filter(richness == min(richness)) %>%
      pivot_longer(c(w_avg_tlvl), names_to = "variable",
        values_to = "variable_values") %>%
      mutate(variable = var_replacement()[variable],
        label = c("b", "c")
      )
    ),
  tar_target(p_fig3,
    plot_grid(
      p_pred_sr_resp_div +
        theme(
          legend.position = "bottom",
          legend.title = element_text(vjust = .75),
          legend.key.width = unit(2.0, "cm")
          ) +
        geom_label(
          data = data_label_pred_show,
          aes(color = NULL, fill = NULL, label = label),
          fontface = "bold"
          ),
        plot_grid(NULL,p_pred_data_show_low_resp,
          p_pred_data_show_high_resp, NULL,
          labels = c("", "b", "c", ""), nrow = 1,
          rel_widths = c(.25, 1, 1, .25)
          ),
        labels = c("a"),
        rel_heights = c(1, .75),
        nrow = 2
    )
    ),
  tar_target(p_fig3_file,
    ggsave_multiple(
      paste0("p_fig3", c(".png", ".pdf")),
      plot = p_fig3,
      path = here::here("report", "figures"),
      scale = 2.6,
      dpi = 400,
      width = 80,
      height = 80 * .8,
      units = "mm")
  )
)
```

@@

@@

```{targets check-model-pred-sr}
list(
  tar_target(model_fw_stab_comp_wo_int,
    lm(stab_com ~ richness + resp_div + env_stoch + ct_alive + w_avg_tlvl + Z +
      avg_int_strength + c, data = sim_fw_sem)),
  tar_target(tab_model_fw_stab_comp_wo_int_vif,
    model_fw_stab_comp_wo_int %>%
      performance::check_collinearity() %>%
      as_tibble() %>%
      mutate(Term = var_replacement()[Term]) %>%
      mutate(VIF = round(VIF, 1)) %>%
      select(Term, VIF) %>%
      kable(
        caption = "Variance Inflation Factor for the linear model predicting the
        relationship between stability and richness.") %>%
        kable_styling()
      ),
    tar_target(sim_res_model_fw_stab_comp,
      model_fw_stab_comp %>%
        mutate(
          res = map(model, DHARMa::simulateResiduals),
          ) %>%
      select(-model)
    ),
    tar_target(plot_diagnotisc_model_fw_stab_comp,
    {
      p <- map(sim_res_model_fw_stab_comp$res,
            function(x) {
              plot(x)
              out <- recordPlot()
              ggdraw(out)
            }
      )
      plot_grid(plotlist = p,
        nrow = 3,
        labels = "auto")
      }),
  tar_target(p_diagnotisc_model_fw_stab_comp_file,
    ggsave_multiple(
      paste0("p_diagnotisc_model_fw_stab_comp", c(".png", ".pdf")),
      plot = plot_diagnotisc_model_fw_stab_comp,
      path = here::here("report", "figures"),
      scale = 2.4,
      dpi = 400,
      width = 80,
      height = 80 * 1.8,
      units = "mm")
  )
)
```

@@

```{r fig-sem}
ggsave_multiple(
  paste0("p_sem_tot", c(".jpg", ".png", ".pdf")),
  plot = p_sem_tot,
  path = here::here("report", "figures"),
  scale = 2.4,
  dpi = 400,
  width = 80,
  height = 80 * 1.6,
  units = "mm")
```
```{r fig-sem-tot-sensibility}
ggsave_multiple(
  paste0("p_sem_simplified_eff_tab_tot", c(".jpg", ".png", ".pdf")),
  plot = tar_read(p_sem_simplified_eff_tab_tot),
  path = here::here("report", "figures"),
  scale = 2.4,
  dpi = 400,
  width = 80,
  height = 80 * .5,
  units = "mm")
```

>>>>

```{targets sem-process}
list(
  tar_target(sim_fw, sim_fw_csc_rerun),
  tar_target(sim_fw_sem,
    sim_fw %>%
      as.data.frame() %>%
      mutate(across(c(stab_com, pop_stab, async, cpe, sae_total, evenness_sae,
            sae_even, cpe_int, cpe_env), log))
    ),
  tar_target(sem_eff,  sem_main_text_eff_csc_rerun),
  tar_target(sem_eff_tab, sem_main_text_eff_tab_csc_rerun),
  tar_target(sem_eff_coeff, sem_main_text_eff_tab_csc_rerun),
  tar_target(tab_sem_coeff,
    sem_main_text_coeff_csc_rerun %>%
      filter(!str_detect(Response, "~~")) %>% #Remove correlation w_avg_tlvl ~~ avg_omnivory
      mutate(across(c("Response", "Predictor"), ~var_replacement()[.x])) %>%
      mutate(Std.Estimate = round(Std.Estimate, 2)) %>%
      rename(`Std estimate` = Std.Estimate) %>%
      select(-Signif)
    ),
  tar_target(sem_collinearity, sem_main_text_collinearity_csc_rerun),
  tar_target(sem_rsquared, sem_main_text_rsquared_csc_rerun),
  tar_target(tab_sem_vif,
    sem_collinearity %>%
      mutate(across(c("response", "Term"), ~var_replacement()[.x])) %>%
      mutate(VIF = round(VIF, 1)) %>%
      select(Response = response, Term, VIF)
    ),
  tar_target(tab_sem_rsquared,
    sem_rsquared %>%
      rename(`$R^2$` = R.squared) %>%
      kable(caption = "Rsquared for the Structural Equation Model.") %>%
      kable_styling()
  ),
  tar_target(tab_sem_simplified_eff,
    sem_simplified_eff_tab %>%
      filter(effect_type == "direct") %>%
      mutate(across(c("response", "predictor"), ~var_replacement()[.x])) %>%
      mutate(effect = round(effect, 2)) %>%
      select(
        Response = response,
        Predictor = predictor,
        `Std estimate` = effect
      )
  )
)
```

@@

```{targets group-all-analysis}
list(
  tar_target(sem_main_text_tot,
    tibble(
      sim_type = c(
        "rerun",
        "non_allo",
        "rebuild",
        "kno"),
      eff = list(
        sem_main_text_eff_tab_csc_rerun,
        sem_main_text_eff_tab_csc_non_allo,
        sem_main_text_eff_tab_csc_rebuild,
        sem_main_text_eff_tab_csc_kno
        ),
      collinearity = list(
        sem_main_text_collinearity_csc_rerun,
        sem_main_text_collinearity_csc_non_allo,
        sem_main_text_collinearity_csc_rebuild,
        sem_main_text_collinearity_csc_kno
        ),
    )
  ),
  tar_target(sem_main_text_eff_tab_tot,
    sem_main_text_tot %>%
      select(sim_type, eff) %>%
      unnest(cols = eff)),
  tar_target(p_sem_main_text_eff_tab_tot,
    sem_main_text_eff_tab_tot %>%
      filter(effect_type == "total") %>%
      filter(response %in% c("async", "pop_stab", "stab_com")) %>%
      filter(predictor %in% sem_tot_predictor()) %>%
      mutate(
        response = recode_factor(response, !!!var_replacement(), .ordered = TRUE),
        predictor = recode_factor(predictor, !!!var_replacement()[rev(sem_tot_predictor())], .ordered = TRUE),
        sim_type = recode_factor(sim_type, !!!sim_type_replacement(), .ordered = TRUE)
        ) %>%
      ggplot(aes(
          y = predictor,
          x = effect,
          color = response,
          shape = sim_type
        )
        ) +
      geom_point(alpha = .5) +
      scale_colour_manual(values = stab_color()) +
      scale_alpha_manual(values = stab_alpha()) +
      #  geom_hline(yintercept = 0, linetype = "dashed") +
      geom_vline(xintercept = 0, linetype = "dashed") +
      facet_grid(cols = vars(response)) +
      labs(
        x = "Total standardised effects",
        color = "Stability component",
        alpha = "Stability component"
        ) +
      theme_bw() +
      theme(
        axis.title.y = element_blank(),
        #legend.justification = "right",
        legend.position = "bottom") +
      guides(
        color = FALSE
        ) +
      theme(
        legend.title = element_blank(),
        legend.position = "bottom",
        legend.justification = c("left", "top")
      )
  )
)
```

@@

```{targets fig-stab-sr}
list(
  tar_target(richness_gradient_pred_show, seq(1, 30, length.out = 20)),
  tar_target(pred_data_show, {
    low_resp_example <- rbind(default_variable_values_pred) %>%
      as_tibble() %>%
      mutate(resp_div = .1, w_avg_tlvl = 2.0, fw_id = "new") %>%
      slice(rep(1, length(richness_gradient_pred_show))) %>%
      mutate(richness = richness_gradient_pred_show)
    high_resp_example <- rbind(default_variable_values_pred) %>%
      as_tibble() %>%
      mutate(resp_div = .9, w_avg_tlvl = 1.2, fw_id = "new") %>%
      slice(rep(1, length(richness_gradient_pred_show))) %>%
      mutate(richness = richness_gradient_pred_show)
    out <- rbind(low_resp_example, high_resp_example)
    out$stab_com <- predict(
      model_fw_stab_comp[model_fw_stab_comp$response == "stab_com", ]$model[[1]],
      out,
      allow.new.levels = TRUE
    )
    out
  }
    ),
  tar_target(p_pred_data_show_low_resp,
    pred_data_show %>%
      filter(resp_div == .1) %>%
      ggplot(aes(x = richness, y = exp(stab_com))) +
      geom_line(color = resp_div_cat_colors()["Low"]) +
      ylim(10, 25) +
      labs(x = "Species richness", y = "Community stability") +
      theme_half_open()
    ),
  tar_target(p_pred_data_show_low_resp_file,
    ggsave_multiple(
      paste0("p_pred_data_show_low_resp", c(".png", ".pdf")),
      plot = p_pred_data_show_low_resp,
      path = here::here("report", "figures"),
      scale = 1.4,
      dpi = 400,
      width = 80,
      height = 80 * .9,
      units = "mm")
    ),
  tar_target(p_pred_data_show_high_resp,
    pred_data_show %>%
      filter(resp_div == .9) %>%
      ggplot(aes(x = richness, y = exp(stab_com))) +
      geom_line(color = resp_div_cat_colors()["High"]) +
      ylim(10, 25) +
      labs(x = "Species richness", y = "Community stability") +
      theme_half_open()
    ),
  tar_target(p_pred_data_show_high_resp_file,
    ggsave_multiple(
      paste0("p_pred_data_show_high_resp", c(".png", ".pdf")),
      plot = p_pred_data_show_high_resp,
      path = here::here("report", "figures"),
      scale = 1.4,
      dpi = 400,
      width = 80,
      height = 80 * .9,
      units = "mm")
    ),
  tar_target(data_label_pred_show,
    pred_data_show %>%
      select(resp_div, richness, w_avg_tlvl) %>%
      filter(richness == min(richness)) %>%
      pivot_longer(c(w_avg_tlvl), names_to = "variable",
        values_to = "variable_values") %>%
      mutate(variable = var_replacement()[variable],
        label = c("b", "c")
      )
    ),
  tar_target(p_fig3,
    plot_grid(
      p_pred_sr_resp_div +
        theme(
          legend.position = "bottom",
          legend.title = element_text(vjust = .75),
          legend.key.width = unit(2.0, "cm")
          ) +
        geom_label(
          data = data_label_pred_show,
          aes(color = NULL, fill = NULL, label = label),
          fontface = "bold"
          ),
        plot_grid(NULL,p_pred_data_show_low_resp,
          p_pred_data_show_high_resp, NULL,
          labels = c("", "b", "c", ""), nrow = 1,
          rel_widths = c(.25, 1, 1, .25)
          ),
        labels = c("a"),
        rel_heights = c(1, .75),
        nrow = 2
    )
    ),
  tar_target(p_fig3_file,
    ggsave_multiple(
      paste0("p_fig3", c(".png", ".pdf")),
      plot = p_fig3,
      path = here::here("report", "figures"),
      scale = 2.6,
      dpi = 400,
      width = 80,
      height = 80 * .8,
      units = "mm")
  )
)
```

@@

```{targets p_sem_main_text_eff_tab_tot_file, tar_simple = TRUE}
ggsave_multiple(
  paste0("p_sem_main_text_eff_tab_tot", c(".png", ".pdf")),
  plot = p_sem_main_text_eff_tab_tot,
  path = here::here("report", "figures"),
  scale = 2.4,
  dpi = 400,
  width = 80,
  height = 80 * .5,
  units = "mm"
  )
```

@@

```{targets check-model-pred-sr}
list(
  tar_target(model_fw_stab_comp_wo_int,
    lm(stab_com ~ richness + resp_div + env_stoch + ct_alive + w_avg_tlvl + Z +
      avg_int_strength + c, data = sim_fw_sem)),
  tar_target(tab_model_fw_stab_comp_wo_int_vif,
    model_fw_stab_comp_wo_int %>%
      performance::check_collinearity() %>%
      as_tibble() %>%
      mutate(Term = var_replacement()[Term]) %>%
      mutate(VIF = round(VIF, 1)) %>%
      select(Term, VIF)
      ),
    tar_target(sim_res_model_fw_stab_comp,
      model_fw_stab_comp %>%
        mutate(
          res = map(model, DHARMa::simulateResiduals),
          ) %>%
      select(-model)
    ),
    tar_target(plot_diagnotisc_model_fw_stab_comp,
    {
      p <- map(sim_res_model_fw_stab_comp$res,
            function(x) {
              plot(x)
              out <- recordPlot()
              ggdraw(out)
            }
      )
      plot_grid(plotlist = p,
        nrow = 3,
        labels = "auto")
      }),
  tar_target(p_diagnotisc_model_fw_stab_comp_file,
    ggsave_multiple(
      paste0("p_diagnotisc_model_fw_stab_comp", c(".jpg", ".pdf")),
      plot = plot_diagnotisc_model_fw_stab_comp,
      path = here::here("report", "figures"),
      scale = 2.4,
      dpi = 400,
      width = 80,
      height = 80 * 1.8,
      units = "mm")
  )
)
```

@@

```{r fig-sem}
ggsave_multiple(
  paste0("p_sem_tot", c(".jpg", ".png", ".pdf")),
  plot = p_sem_tot,
  path = here::here("report", "figures"),
  scale = 2.4,
  dpi = 400,
  width = 80,
  height = 80 * 1.6,
  units = "mm")
```
